The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs

### 2022-03-09 src/paper.tex
Add preliminary science draft.
Final version.
Headline, first batch of changes.
Version as submitted.
Various fixes that got lost in the previous PR.
Add declaration of competing interests.
Add declaration of interest.
Title consistent.

\newcommand{\papertitle}{
The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs
}

@@

\begin{refcontext}[sorting=nyt]  % Sort BIBLIOGRAPHY by alphabet (while CITATIONS are sorted by year)
\printbibliography[heading=bibintoc]
\end{refcontext}

@@

    \input{paper/appendix_data}

@@

    \input{paper/appendix_model}

    \input{paper/appendix_results}

    \printbibliography[heading=bibintoc]

>>>>

\newcommand{\papertitle}{
    The Effectiveness of Antigen Rapid Diagnostic Tests, Vaccinations, and Contact Restrictions for Containing the Covid-19 Pandemic
}

@@

\begin{refcontext}[sorting=none]  % Sort BIBLIOGRAPHY by appearance.
    \printbibliography[heading=bibintoc]
\end{refcontext}

\section*{Ethical declarations}

\subsection*{Competing interests}

The authors declare no competing interests.

@@

        \input{paper/appendix_materials_and_methods}

@@

        \input{paper/appendix_supplementary_text}

        \begin{refcontext}[sorting=none]
            \printbibliography[heading=bibintoc]
        \end{refcontext}

### 2022-03-09 src/rev1_reply_comments.tex
Title consistent.

\title{\large Reply to the Editor's and Reviewers' comments on: \\[2ex]
    \LARGE The Effectiveness of Antigen Rapid Diagnostic Tests, Vaccinations and Contact Restrictions for Containing the Covid-19 Pandemic\\[2ex]
    \large Submitted to Scientific Reports (Submission ID db917d3c-b56a-4129-8eb1-a62a716aaede)\\[-6ex]
}

@@

\comment{
The title should have a clear, precise scientific meaning and should not contain a colon. Where possible, the title should be read as one concise sentence.
}
\vskip1ex
\response{%
    We changed the title from ``The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs'' to ``The Effectiveness of Antigen Rapid Diagnostic Tests, Vaccinations and Contact Restrictions for Containing the Covid-19 Pandemic''
}

>>>>

\title{\large Reply to the Editor's and Reviewers' comments on: \\[2ex]
    \LARGE The Effectiveness of Antigen Rapid Diagnostic Tests, Vaccinations, and Contact Restrictions for Containing the Covid-19 Pandemic\\[2ex]
    \large Submitted to Scientific Reports (Submission ID db917d3c-b56a-4129-8eb1-a62a716aaede)\\[-6ex]
}

@@

\comment{
The title should have a clear, precise scientific meaning and should not contain a colon. Where possible, the title should be read as one concise sentence.
}
\vskip1ex
\response{%
    We changed the title from ``The Effectiveness of Strategies to Contain SARS-CoV-2: Testing, Vaccinations, and NPIs'' to ``The Effectiveness of Antigen Rapid Diagnostic Tests, Vaccinations, and Contact Restrictions for Containing the Covid-19 Pandemic''
}
